TRITON: Globally Consistent Sim-to-Real Transfer

### 2022-06-04 CORL/example.tex
Fixed typo

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/unprojection_consistency_loss.pdf}
	\end{center}
	\caption{
		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
		we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...R,\ 1...L}$ .
		If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
		We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$ , then averaging the result.
		When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
		Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
	}
	\label{fig:unprojection_consistency_loss}
\end{figure}

>>>>

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/unprojection_consistency_loss.pdf}
	\end{center}
	\caption{
		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
		we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...B,\ 1...L}$ .
		If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
		We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$ , then averaging the result.
		When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
		Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
	}
	\label{fig:unprojection_consistency_loss}
\end{figure}
